SciPy 1.0---Fundamental Algorithms for Scientific Computing in Python

### 2019-03-01 scipy-1.0/paper.tex
benchmark suite refers to test suite -> put test suite first.

@@

The airspeed velocity (\texttt{asv}\cite{asvref}) library enables benchmarking Python packages
over their lifetimes, and the performance of the SciPy codebase was monitored
with \texttt{asv} starting in February of 2015 (PR \#4501). In addition to ensuring that
unit tests are passing (see Test suite section below), confirming 
that performance generally
remains constant or improves over the commit hash history of the project allows
us to objectively measure that our codebase is improving.

@@

\subsubsection*{Test suite}

>>>>

\subsubsection*{Test suite}
\label{sec:testsuite}

@@

The airspeed velocity (\texttt{asv}\cite{asvref}) library enables benchmarking Python packages
over their lifetimes, and the performance of the SciPy codebase was monitored
with \texttt{asv} starting in February of 2015 (PR \#4501). In addition to ensuring that
unit tests are passing (see section \ref{sec:testsuite}), confirming 
that performance generally
remains constant or improves over the commit hash history of the project allows
us to objectively measure that our codebase is improving.

@@
